Discrete Time Markov Model

### 2025-06-24 analysis/discrete-markov.qmd
Update

sapply(files, source)

@@

```{r long_data}
data_stack <- data_stack |>
  inner_join(data[, cols], by = "ID") |>
  # Removing baseline age below 60
  filter(Age - (2022 - 2016) >= 60) |>
  pivot_and_factorise(time_vary = FALSE) |>
  group_by(ID) |>
  # ^ Make age time varying
  mutate(Age = Age - (2022 - as.numeric(as.character(wave))))

@@

stationary_results <- rbind(tidy_output(fit_3a), tidy_output(fit_3b)) |>
  rename(transition = y.level) |>
  mutate(
    # Transforming to odds ratios
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high),

    # Mutating to factors
    transition = factor(
      transition, 
      levels = c("NC - MCI", "MCI - NC", 
                 "NC - Dementia", "MCI - Dementia")),
    term = factor(
      term, 
      levels = c("Being female", "Age", "High school degree vs. No education",
                 "Further education vs. No education", "Depression",
                 "Procrastination (2020)", "Previous state: MCI", 
                 "Previous state: Dementia")),

    # Creating a colour code
    colour = case_when(
      estimate > 1 & p.value < 0.05 ~ "Positive",
      estimate < 1 & p.value < 0.05 ~ "Negative",
      TRUE ~ "NS"),

    colour = factor(colour, levels = c("Positive", "Negative", "NS"))
    )

@@

```{r}
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 12
#| label: fig-model-predictions
#| fig-cap: "Predicted transition probabilities from the stationary model."
#| 
## Making a prediction dataset -------------------------------------------------
pred_data <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

@@

# Getting estimated probabilities
estimated_probs <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression),
  Total_p = mean(data_stack$Total_p),
  status_prev = states) |>
  modelr::add_predictions(model = fit_3a, var = "pred", type = "probs")

@@

interaction_results <- rbind(tidy_output(fit_4a), tidy_output(fit_4b)) |>
  rename(transition = y.level) |>
  mutate(
    # Transforming to odds ratios
    estimate = exp(estimate),
    conf.low = exp(conf.low),
    conf.high = exp(conf.high),

    # Mutating to factors
    transition = factor(
      transition, 
      levels = c("NC - MCI", "MCI - NC", 
                 "NC - Dementia", "MCI - Dementia")),
    term = factor(
      term, 
      levels = c("Being female", "Age", 
                 "High school degree vs. No education",
                 "Further education vs. No education", "Depression",
                 "Procrastination (2020)",  
                 "Age x Procrastination", "Previous state: MCI", 
                 "Previous state: Dementia")),

    # Creating a colour code
    colour = case_when(
      estimate > 1 & p.value < 0.05 ~ "Positive",
      estimate < 1 & p.value < 0.05 ~ "Negative",
      TRUE ~ "NS"),

    colour = factor(colour, levels = c("Positive", "Negative", "NS"))
    )

interaction_results |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 3))) |>
  DT::datatable(
    options = list(
      pageLength = 6,
      dom = "tip",
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE
  )
```

@@

# Making a new predicted dataset
pred_data <- expand.grid(
  Gender = factor(0),
  Age = seq(60, 97, length = 200),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

@@

# Create predictions with age info
age_cohots <- expand.grid(
  Gender = factor(0),
  Age = c(60, 70, 80, 90),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200)) |>
  modelr::add_predictions(model = fit_4a, var = "pred", type = "probs") |>
  tidy_predictions() |>
  filter(status_prev %in% c("Normal Cognition", "MCI") & 
         status %in%  c("Normal Cognition", "MCI"))

# Identifying right most point for each label point
label_data <- age_cohots |>
  group_by(status_prev, Age) |>
  filter(Total_p == max(Total_p)) |>
  ungroup()

# Plotting ---------------------------------------------------------------------
ggplot(data = age_cohots, aes(x = Total_p, y = prob, colour = Age)) +
  geom_line(linewidth = 1) + 
  ggrepel::geom_text_repel(
    data = label_data,
    aes(label = paste0("Age ", Age), colour = factor(Age)),
    direction = "y", nudge_x = 4, hjust = 0,
    segment.size = 0.2, segment.colour = "grey50",
    size = 3.5, show.legend = FALSE) +
  scale_x_continuous(
    breaks = seq(0, 60, by = 10),
    sec.axis = sec_axis(
      ~., name = "Previous State",
      breaks = NULL, labels = NULL)) +
  scale_y_continuous(
    sec.axis = sec_axis(
      ~ ., name = "Current State",
      breaks = NULL, labels = NULL)) +
  ggokabeito::scale_color_okabe_ito() +
  labs(
    title = "Predicted transition probabilities for different age cohorts",
    x = "Procrastination", y = "Probability", colour = NULL) +
  facet_grid(status ~ status_prev) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none")

@@

# Model 4: Additive time effects
fit_4a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + status_prev + wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_4b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + status_prev + wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 5: State-specific time effects
fit_5a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (status_prev * wave), family = multinomial, 
  data = data_stack, trace = FALSE)

fit_5b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (status_prev * wave), family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 6: Full time interactions
fit_6a <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Depression + Total_p + status_prev) * wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_6b <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Depression + Total_p + status_prev) * wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)
```

@@

# Fit statistics
models <- list(
  "Stationary" = fit_3a,
  "Additive Time" = fit_4a,
  "State-Time Interaction" = fit_5a,
  "Full Interactions" = fit_6a
)

@@

# Outputting as table
anova(fit_3a, fit_4a, fit_5a, fit_6a) |>
  mutate(
    Model = c("Stationary", "Additive", "State-Time Interactions", "Full Interactions"),
    `Resid. Dev` = round(`Resid. Dev`, digits = 3),
    `LR stat.` = round(`LR stat.`, digits = 3),
    `Pr(Chi)` = round(`Pr(Chi)`, digits = 3)
    ) |>
  cbind(comparison_table) |>
  DT::datatable(
    options = list(
      pagelength = 4,
      dom = "t",
      ordering = FALSE,
      columnDefs = list(list(className = 'dt-center', targets = "_all"))
    ),
    rownames = FALSE
  )
```

@@

```{r non-stationary-output}
additive_results <- rbind(tidy_output(fit_4a), tidy_output(fit_4b))

additive_results |>
  rename(transiton = y.level) |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 3))) |>
  DT::datatable(
    options = list(
      pageLength = 6,
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE,
    colnames = c("Transition", "Predictor", "Estimate", "Standard Error",
                 "Statistic", "p-val", "Lower CI", "Upper CI")
  )
```

@@

create_additive_predictions(data = data_stack, model = fit_4a, var = "Age", var_seq = seq(50, 97, by = 5)) |>
  plot_additive_predictions(var = "Age", x_label = "Age", subtitle = "By Age")

@@

create_additive_predictions(data = data_stack, model = fit_4a, var = "Total_dep_2016", var_seq = seq(0, 8, by = 1)) |>
  plot_additive_predictions(var = "Total_dep_2016", x_label = "Depression", subtitle = "By depression")

@@

create_additive_predictions(data = data_stack, model = fit_4a, var = "Education_tri", var_seq = factor(c(0:2)), hold_constant = list(Gender = factor(0))) |>
  plot_additive_predictions(var = "Education_tri", x_label = "Education", subtitle = "By education level") +
  geom_point(size = 2) +
  scale_x_continuous(breaks = c(0, 1, 2), labels = c("No Education", "High School", "Further Education")) +
  theme(axis.text.x = element_text(size = 8, angle = 60, vjust = 0.90, hjust = 1))
```

@@

create_additive_predictions(data = data_stack, model = fit_4a, var = "Total_p", var_seq = seq(0, 60, by = 1)) |>
  plot_additive_predictions(var = "Total_p", x_label = "Procrastination", subtitle = "By procrastination")

```
:::

@@

```{r multiplicative-output}
multiplicative_output <- rbind(
  tidy_output(fit_6a, multiplicative = TRUE),
  tidy_output(fit_6b, multiplicative = TRUE))

multiplicative_output |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 3))) |>
  DT::datatable(
    options = list(
      pageLength = 6,
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE,
    colnames = c("Transition", "Predictor", "Estimate", "Standard Error",
                 "Statistic", "p-val", "Lower CI", "Upper CI")
  )

```
:::

>>>>

purrr::walk(files, source)

@@

```{r long_data}
data_stack <- data_stack |>
  inner_join(data[, cols], by = "ID") |>
  # Removing baseline age below 60
  filter(Age - (2022 - 2016) >= 60) |>
  pivot_and_factorise(time_vary = TRUE) |>
  group_by(ID) |>
  # ^ Make age time varying
  mutate(Age = Age - (2022 - as.numeric(as.character(wave))))

@@

stationary_results <- rbind(tidy_output(fit_3a), tidy_output(fit_3b)) |>
  mutate(
    # Mutating to factors
    transition = factor(
      transition, 
      levels = c("NC - MCI", "MCI - NC", 
                 "NC - Dementia", "MCI - Dementia")),
    term = factor(
      term, 
      levels = c("Being female", "Age", "High school degree vs. No education",
                 "Further education vs. No education", "Depression",
                 "Procrastination (2020)", "Previous state: MCI", 
                 "Previous state: Dementia"))
    )

@@

```{r}
#| code-fold: true
#| code-summary: "Check out my code"
#| fig-width: 12
#| label: fig-model-predictions
#| fig-cap: "Predicted transition probabilities from the stationary model."
#| 
## Making a prediction dataset -------------------------------------------------
pred_data <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression, na.rm = TRUE),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

@@

# Getting estimated probabilities
estimated_probs <- expand.grid(
  Gender = factor(0),
  Age = mean(data_stack$Age),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression, na.rm = TRUE),
  Total_p = mean(data_stack$Total_p),
  status_prev = states) |>
  modelr::add_predictions(model = fit_3a, var = "pred", type = "probs")

@@

interaction_results <- rbind(tidy_output(fit_4a), tidy_output(fit_4b)) |>
  mutate(
    # Mutating to factors
    transition = factor(
      transition, 
      levels = c("NC - MCI", "MCI - NC", 
                 "NC - Dementia", "MCI - Dementia")),
    term = factor(
      term, =
      levels = c("Being female", "Age", 
                 "High school degree vs. No education",
                 "Further education vs. No education", "Depression",
                 "Procrastination (2020)",  
                 "Age x Procrastination", "Previous state: MCI", 
                 "Previous state: Dementia")),
    )

interaction_results |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 4))) |>
  DT::datatable(
    options = list(
      pageLength = 10,
      dom = "tip",
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE
  )
```

@@

# Making a new predicted dataset
pred_data <- expand.grid(
  Gender = factor(0),
  Age = seq(60, 97, length = 200),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression, na.rm = TRUE),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200))

@@

# Create predictions with age info
age_cohots <- expand.grid(
  Gender = factor(0),
  Age = c(62:97),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression, na.rm = TRUE),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200)) |>
  modelr::add_predictions(model = fit_4a, var = "pred", type = "probs") |>
  tidy_predictions() |>
  filter(status_prev %in% c("Normal Cognition", "MCI") &
         status %in%  c("Normal Cognition", "MCI")) |>
  mutate(label = case_when(
    Age %in% c(70, 80, 90) ~ as.character(Age), 
    TRUE ~ "Other"
  ))

# Identifying right most point for each label point
label_data <- age_cohots |>
  filter(Age %in% c(70, 80, 90)) |>
  group_by(status_prev, Age) |>
  filter(Total_p == max(Total_p)) |>
  ungroup()

# Plotting ---------------------------------------------------------------------
ggplot(data = age_cohots, aes(x = Total_p, y = prob, 
                              group = interaction(Age, status_prev, status),
                              colour = label)) +
  geom_line(aes(linewidth = label)) + 
  ggrepel::geom_text_repel(
    data = label_data,
    aes(label = paste0("Age ", Age), colour = as.character(Age)),
    direction = "y", nudge_x = 4, hjust = 0,
    segment.size = 0.5, segment.colour = "grey50",
    size = 3, show.legend = FALSE) +
  scale_x_continuous(
    breaks = seq(0, 60, by = 10),
    sec.axis = sec_axis( ~., name = "Previous State", breaks = NULL, labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis( ~ ., name = "Current State", breaks = NULL, labels = NULL)) +
  scale_colour_manual(values = c(
    "70"    = "#E69F00", 
    "80"    = "#56B4E9", 
    "90"    = "#009E73",
    "Other" = "grey80")) +
  scale_linewidth_manual(values = c(
    "70"    = 1.5, 
    "80"    = 1.5, 
    "90"    = 1.5,
    "Other" = 0.5)) +
  labs(
    title = "Predicted transition probabilities for different age cohorts",
    x = "Procrastination", y = "Probability", colour = NULL) +
  facet_grid(status ~ status_prev) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none")
```

@@

# Model 5: Additive time effects
fit_5a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) +  status_prev + wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_5b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) + status_prev + wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 6: State-specific time effects
fit_6a <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) + (status_prev * wave), family = multinomial, 
  data = data_stack, trace = FALSE)

fit_6b <- nnet::multinom(
  status ~ Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) + (status_prev * wave), family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)

# Model 7: Full time interactions
fit_7a <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) + status_prev) * wave, family = multinomial, 
  data = data_stack, trace = FALSE)

fit_7b <- nnet::multinom(
  status ~ (Gender + Age + Education_tri + Depression + Total_p + (Total_p * Age) + status_prev) * wave, family = multinomial, 
  data = data_stack |> mutate(status = relevel(status, ref = 2)), 
  trace = FALSE)
```

@@

# Fit statistics
models <- list(
  "Interaction" = fit_4a,
  "Additive Time" = fit_5a,
  "State-Time Interaction" = fit_6a,
  "Full Interactions" = fit_7a
)

@@

# Outputting as table
anova(fit_4a, fit_5a, fit_6a, fit_7a) |>
  mutate(
    Model = c("Interaction", "Additive", "State-Time Interactions", "Full Interactions"),
    `Resid. Dev` = round(`Resid. Dev`, digits = 3),
    `LR stat.` = round(`LR stat.`, digits = 3),
    `Pr(Chi)` = round(`Pr(Chi)`, digits = 3)
    ) |>
  cbind(comparison_table) |>
  DT::datatable(
    options = list(
      pagelength = 4,
      dom = "t",
      ordering = FALSE,
      columnDefs = list(list(className = 'dt-center', targets = "_all"))
    ),
    rownames = FALSE
  )
```

@@

```{r non-stationary-output}
additive_results <- rbind(tidy_output(fit_5a), tidy_output(fit_5b))

additive_results |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 3))) |>
  DT::datatable(
    options = list(
      pageLength = 6,
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE,
    colnames = c("Transition", "Predictor", "Estimate", "Standard Error",
                 "Statistic", "p-val", "Lower CI", "Upper CI")
  )
```

@@

create_additive_predictions(data = data_stack, model = fit_5a, var = "Age", var_seq = seq(50, 97, by = 5)) |>
  plot_additive_predictions(var = "Age", x_label = "Age", subtitle = "By Age")

@@

create_additive_predictions(data = data_stack, model = fit_5a, var = "Depression", var_seq = seq(0, 8, by = 1)) |>
  plot_additive_predictions(var = "Depression", x_label = "Depression", subtitle = "By depression")

@@

create_additive_predictions(data = data_stack, model = fit_5a, var = "Education_tri", var_seq = factor(c(0:2)), hold_constant = list(Gender = factor(0))) |>
  plot_additive_predictions(var = "Education_tri", x_label = "Education", subtitle = "By education level") +
  geom_point(size = 2) +
  scale_x_continuous(breaks = c(0, 1, 2), labels = c("No Education", "High School", "Further Education")) +
  theme(axis.text.x = element_text(size = 8, angle = 60, vjust = 0.90, hjust = 1))
```

@@

create_additive_predictions(data = data_stack, model = fit_5a, var = "Total_p", var_seq = seq(0, 60, by = 1)) |>
  plot_additive_predictions(var = "Total_p", x_label = "Procrastination", subtitle = "By procrastination")

## Interaction

```{r}
#| code-fold: true
#| code-summary: "Check our my code"
#| fig-width: 12
#| fig-height: 10
#| label: fig-non-stationary-interaction
#| fig-cap: "Predicted transition probabilities from the non-stationary model (interaction effect)."

# Making prediction dataset ----------------------------------------------------
pred_data <- expand.grid(
  Gender = factor(0),
  Age = c(62:97),
  Education_tri = factor(0),
  Depression = mean(data_stack$Depression),
  status_prev = levels(data_stack$status_prev),
  Total_p = seq(0, 60, length = 200),
  wave = c(2:4)
) |>
  modelr::add_predictions(model = fit_5a, var = "pred", type = "prob") |>
  tidy_predictions() |>
  filter(status_prev != "Dementia", status != "Dementia") |>
  mutate(label = case_when(
    Age %in% c(70, 80, 90) ~ as.character(Age), 
    TRUE ~ "Other"
  ))

# For adding age labels --------------------------------------------------------
label_data <- pred_data |>
  filter(Age %in% c(70, 80, 90)) |>
  group_by(status_prev, Age) |>
  filter(Total_p == max(Total_p)) |>
  ungroup()

pred_data |>
  ggplot(aes(x = Total_p, y = prob, 
             group = interaction(Age, status_prev, status),
             colour = label)) +
  geom_line(aes(linewidth = label)) +
  ggrepel::geom_text_repel(
    data = label_data,
    aes(label = paste0("Age ", Age), colour = as.character(Age)),
    direction = "y", nudge_x = 4, hjust = 0,
    segment.size = 1, segment.colour = "grey50",
    size = 2.5, show.legend = FALSE) +
  scale_x_continuous(
    breaks = seq(0, 60, by = 10), expand = expansion(mult = c(0, 0.2)),
    sec.axis = sec_axis( ~., name = "Previous State", breaks = NULL, labels = NULL)) +
  scale_y_continuous(sec.axis = sec_axis( ~ ., name = "Current State", breaks = NULL, labels = NULL)) +
  scale_colour_manual(values = c(
    "70"    = "#E69F00", 
    "80"    = "#56B4E9", 
    "90"    = "#009E73",
    "Other" = "grey80")) +
  scale_linewidth_manual(values = c(
    "70"    = 1.5, 
    "80"    = 1.5, 
    "90"    = 1.5,
    "Other" = 0.5)) +
  labs(
    title = "Predicted transition probabilities for different age cohorts",
    subtitle = "Across time",
    x = "Procrastination", y = "Probability", colour = NULL) +
  facet_grid(status ~ status_prev + wave, labeller = labeller(
    wave = c("2" = "2016 - 2018", "3" = "2018 - 2020", "4" = "2020 - 2022"),
  )) +
  theme_bw() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
    plot.subtitle = element_text(hjust = 0.5, size = 14, face = "bold"),
    axis.title = element_text(size = 12, face = "bold"),
    strip.text = element_text(size = 9, face = "bold"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    legend.title = element_text(size = 10, face = "bold"),
    legend.position = "none")

@@

```{r multiplicative-output}
multiplicative_output <- rbind(
  tidy_output(fit_7a, multiplicative = TRUE),
  tidy_output(fit_7b, multiplicative = TRUE))

multiplicative_output |>
  mutate(across(c(estimate, conf.low, conf.high), ~ round(x = ., digits = 3))) |>
  DT::datatable(
    options = list(
      pageLength = 6,
      ordering = FALSE,
      columnDefs = list(list(className = "dt-center", targets = "_all"))
    ),
    rownames = FALSE,
    colnames = c("Transition", "Predictor", "Estimate", "Standard Error",
                 "Statistic", "p-val", "Lower CI", "Upper CI", "colour")
  )
```

```{r}
multiplicative_output |>
  filter(!term %in% c("Previous state: MCI", "Previous state: Dementia", "Previous state: MCI & Time", "Previous state: Dementia & Time")) |>
  ggplot(aes(x = estimate, y = transition, colour = colour)) +
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey50") +
    ggstance::geom_pointrangeh(
    aes(xmin = conf.low, xmax = conf.high),
    position = ggstance::position_dodgev(height = 0.5),
    size = 1.25,
    fatten = 3) +
  scale_colour_manual(values = c(
    "Positive" = "#0072B2", 
    "Negative" = "#E69F00", 
    "NS"       = "#B2BEB5")) +
  facet_wrap(~term, scales = "free_x")
```
